Windowed Residual-Minimization Model Reduction for Dynamical Systems

### 2019-09-19 section3/general_form.tex
latest

\section{Windowed Least-Squares Formulation}\label{sec:tclspg} This section
outlines the proposed \methodName\ 
formulation (\methodAcronym). In contrast to (1.) the Galerkin method, which minimizes the 
time-instantaneous residual, (2.) the LSPG method, which sequentially minimizes the discrete 
residual over a single time step, and (3.) the ST-LSPG method, which minimizes the discrete 
space--time residual, the proposed \methodAcronym\ method sequentially minimizes the 
time-continuous FOM ODE residual over a series of
\textit{time windows}. The formulation is compatible with both \spatialAcronym\ and \spaceTimeAcronym\ trial spaces. 
In this section, we start by outlining the \methodAcronym\ formulation  
for a general trial space. We then examine the \spatialAcronym\ 
trial space, followed by the \spaceTimeAcronym\ trial space. In each case, we derive the stationary conditions 
associated with the minimization problems.
 %The proposed method can be formulated equivalently from
%two viewpoints. The first formulation corresponds to a sequence of
%minimization problems for the generalized coordinates that minimize the FOM
%ODE residual over each time slab. We refer to this as the 
%\textit{residual-minimization viewpoint}. The second viewpoint corresponds to
%formulating an optimal control problem for the Galerkin ROM. In this
%viewpoint, the \methodAcronym\ method is formulated as an optimal control
%problem in where the objective is to find a ``controller" that minimizes the
%residual of the Galerkin ROM. We refer to this viewpoint as the
%\textit{optimal control viewpoint.}  This section outlines the derivation of the \methodAcronym\ method
%from both the residual minimization and optimal control viewpoints.

%\subsection{Formulation of the Time-Continuous LSPG Method} In contrast to
%the LSPG approach, which minimizes the fully discrete residual over a
%time-step, the present work proposes minimizing the time-continuous FOM ODE
%residual over time slabs. The proposed method can be formulated equivalently
%from two viewpoints. The first approach formulates the problem from a
%standard calculus of variations viewpoint and is analogous to the classic
%residual minimization process used in the LSPG method (but here performed at
%the continuous level). The second viewpoint corresponds to formulating an
%optimal control problem in Lagrange form (which is a specific instance of an
%optimal control problem of Bolza type). In this viewpoint, the
%\methodAcronym\ is formulated as an optimal control problem in where the
%objective is to find a ``controller" that minimizes the residual of the
%Galerkin ROM. We now outline both of these (equivalent) formulations. 
%
\subsection{Residual Minimization Formulation} 
We start by partitioning the
temporal domain into a set of $\nslabs$ windows of size $\DeltaSlabArg{n}$. This partitioning is depicted in Fig.~\ref{fig:slab_fig}.
\begin{figure} 
\begin{centering} 
\includegraphics[trim={0.0cm 5cm 0cm 3cm},clip,width=1.0\textwidth]{figs/time_grid.pdf} \caption{Decomposition of time
domain into time windows.} \label{fig:slab_fig} \end{centering} 
\end{figure}
Over each time window, we introduce the space--time trial space,
$$\approxstate^n \in \stspace^n \subseteq \RR{N} \otimes \timeSpaceArg{n} , \qquad  n = 1,\ldots,\nslabs,$$ 
where $\approxstate^n :  [\timeStartArg{n} , \timeEndArg{n}] \rightarrow
\RR{\fomdim}$
is the \methodAcronym\ approximation to the state over the $n$th time window, $\timeSpaceArg{n}$ is the set of functions acting on $[\timeStartArg{n},\timeEndArg{n}]$, and  
$\timeStartArg{n}$ and $\timeEndArg{n}$ are the beginning and end of the $n$th
time window, respectively. Over each window, define the objective,
%\begin{equation}\label{eq:obj} \mathcal{J}^n(\stateArg{}{t}) = \frac{1}{2}
%\int_{\timeStartArg{n}}^{\timeEndArg{n}} \big[ \dot{\state}(\tau) -
%\velocity(\stateArg{}{\tau}) \big]^T \stweightingMatArg{n}(\tau) \big[
%\dot{\state}(\tau) - \velocity(\stateArg{}{\tau}) \big] d \tau,
%\end{equation}
\begin{equation}\label{eq:obj}
\begin{split} \mathcal{J}^n &\vcentcolon \statey \mapsto
\frac{1}{2} \int_{\timeStartArg{n}}^{\timeEndArg{n}} \big[ \dot{\statey}(t)
- \velocity(\stateyArg{}{t},t) \big]^T \stweightingMatArgt{n}{t} \big[
\dot{\statey}(t) - \velocity(\stateyArg{}{t},t) \big] d t \\
%&\vcentcolon \RR{\fomdim} \times [\timeStartArg{n},\timeEndArg{n}] \rightarrow
%\RR{}, \end{align}
&\vcentcolon \RR{\fomdim}\otimes \timeSpaceArg{n}  \rightarrow
\RR{}, 
\end{split}
\end{equation}
%\begin{align}\label{eq:obj} \mathcal{J}^n &\vcentcolon \state \mapsto
%\frac{1}{2} \int_{\timeStartArg{n}}^{\timeEndArg{n}} \resid(\state)^T
%\stweightingMat \resid(\state) d\tau \\ &\vcentcolon \RR{\fomdim} \times
%[0,T] \rightarrow \RR{}.  \end{align}
where $\stweightingMatArg{n} \equiv \stweightingMatOneArg{ }^T \stweightingMatOneArg{ } \in \RR{\fomdim \times \fomdim}$ is a
symmetric positive semi-definite matrix that, e.g., enables hyper-reduction and/or modifies the norm. For simplicity, 
it is assumed that the weighting matrix is the same for all time windows.

\methodAcronym\ computes a sequence of approximate solutions $\approxstateArgnt{n}$, for $n=1,\ldots,\nslabs$, as the solution to the minimization problems,
\begin{equation}\label{eq:tclsrm}
\begin{split}
      &\underset{\stateyArgnt{n} \in \stspace^n}{\text{minimize}} \; \mathcal{J}^n(\stateyArgnt{n}), \\
      &\text{subject to } \;  \stateyArg{n}{\timeStartArg{n}} =
\begin{cases}\mathbb{P}^n (\approxstateArgnt{n-1})(\timeEndArg{n-1}) & n = 2,\ldots,\nslabs \\
\mathbb{P}^n( \stateFOMArgnt{1})(0)& n=1, \end{cases} 
\end{split}
\end{equation}
%\methodAcronym\ computes a sequence of approximate solutions $\approxstateArgnt{n}$ as the solution to the minimization problem,
%\begin{equation}\label{eq:tclsrm}
%\begin{split}
%       &\approxstateArgnt{n} =  \underset{\statey \in \stspace^n}{\text{arg\,min}} \; \mathcal{J}^n(\statey), \\ 
%      &\text{subject to }\;  \approxstateArg{n}{\timeStartArg{n}} =
%\begin{cases}\mathbb{P}^n (\approxstateArgnt{n-1})(\timeEndArg{n-1}) & n = 2,\ldots,\nslabs \\
%\mathbb{P}^n( \stateFOMArgnt{1})(0)& n=1, \end{cases} 
%\end{split}
%\end{equation}
where $\mathbb{P}^n: \RR{N} \otimes \timeSpaceArg{n} \rightarrow \stspaceArg{n}$ is an orthogonal projection onto the 
trial space (e.g., $\elltwo$).
%\methodAcronym\ generates approximations to~\eqref{eq:FOM} by sequentially minimizing
%the FOM ODE residual over the trial space for each time slab.
%\methodAcronym\ is defined as follows,
%\begin{equation}\label{eq:tclsrm}
%\approxstate^n= \underset{\statey \in \stspace^n}{\text{arg\,min } }
%\mathcal{J}^n(\statey), \qquad n = 1,2,...,\nslabs,
%\end{equation}
% subject to
%the boundary condition, \begin{equation*} \approxstate^n(\timeStartArg{n}) =
%\begin{cases}\mathbb{P}^n \approxstate^{n-1}(\timeEndArg{n-1}) & n = 2,\ldots,\nslabs \\
%\mathbb{P}^n \stateFOMIC & n=1, \end{cases} \end{equation*}
%where $\mathbb{P}^n: \RR{N} \rightarrow \stspaceArg{n}$ projects onto the 
%trial space (e.g., an $L^2$ projector).
\begin{remark}
It is possible to construct the trial spaces such that they have continuous support between time windows through the 
use of, e.g., affine transformations.
\end{remark}
%and 
%$\approxstate^n :  [\timeStartArg{n} , \timeEndArg{n}] \rightarrow
%\RR{\fomdim}$
%is the approximate solution over the $n$th time slab.% and $\approxstate_0 \in
%\RR{\fomdim}$ is the FOM initial condition
%projected onto the trial space; (e.g., via for $L^2$ projection).
We now define the trial spaces $\stspaceArg{n}$. We consider \spatialAcronym\ trial spaces and \spaceTimeAcronym\ trial spaces. 
We leave further investigation into other trial spaces, such as nonlinear manifolds~\cite{leeCarlberg}, as a subject for future work.
%A variety of trial spaces have been examined in the model-order reduction community.
%The most popular trial space comprises a linear, spatial-projection-only trial space (e.g., Eqns.~\eqref{eq:spatial_subspace}-\eqref{eq:spatial_subspace3}), although recently 
%nonlinear trial spaces~\cite{leeCarlberg} and space--time trial spaces~\cite{choi_stlspg,constantine_strom,2,3} have gained attention. This work focuses on the classic 
%spatial-projection-only trial space, and also briefly considers space--time trial spaces.
%We leave further investigation into other trial spaces as future work.

>>>>

\section{Windowed Least-Squares Formulation}\label{sec:tclspg} This section
outlines the proposed \methodNameLower\ 
formulation (\methodAcronym). In contrast to (1.) the Galerkin method, which minimizes the 
time-instantaneous residual, (2.) the LSPG method, which sequentially minimizes the discrete 
residual over a single time step, and (3.) the ST-LSPG method, which minimizes the discrete 
space--time residual, the proposed \methodAcronym\ method sequentially minimizes the 
time-continuous FOM ODE residual over a series of
\textit{time windows}. The formulation is compatible with both \spatialAcronym\ and \spaceTimeAcronym\ trial subspaces. 
In this section, we start by outlining the \methodAcronym\ formulation  
for a general trial subspace. We then examine the \spatialAcronym\ 
trial subspace, followed by the \spaceTimeAcronym\ trial subspace. In each case, we derive the stationary conditions 
associated with the minimization problems.
 %The proposed method can be formulated equivalently from
%two viewpoints. The first formulation corresponds to a sequence of
%minimization problems for the generalized coordinates that minimize the FOM
%ODE residual over each time slab. We refer to this as the 
%\textit{residual-minimization viewpoint}. The second viewpoint corresponds to
%formulating an optimal control problem for the Galerkin ROM. In this
%viewpoint, the \methodAcronym\ method is formulated as an optimal control
%problem in where the objective is to find a ``controller" that minimizes the
%residual of the Galerkin ROM. We refer to this viewpoint as the
%\textit{optimal control viewpoint.}  This section outlines the derivation of the \methodAcronym\ method
%from both the residual minimization and optimal control viewpoints.

%\subsection{Formulation of the Time-Continuous LSPG Method} In contrast to
%the LSPG approach, which minimizes the fully discrete residual over a
%time-step, the present work proposes minimizing the time-continuous FOM ODE
%residual over time slabs. The proposed method can be formulated equivalently
%from two viewpoints. The first approach formulates the problem from a
%standard calculus of variations viewpoint and is analogous to the classic
%residual minimization process used in the LSPG method (but here performed at
%the continuous level). The second viewpoint corresponds to formulating an
%optimal control problem in Lagrange form (which is a specific instance of an
%optimal control problem of Bolza type). In this viewpoint, the
%\methodAcronym\ is formulated as an optimal control problem in where the
%objective is to find a ``controller" that minimizes the residual of the
%Galerkin ROM. We now outline both of these (equivalent) formulations. 
%
\subsection{Residual Minimization Formulation} 
We start by partitioning the
temporal domain into a set of $\nslabs$ windows of size $\DeltaSlabArg{n}$. This partitioning is depicted in Fig.~\ref{fig:slab_fig}.
\begin{figure} 
\begin{centering} 
\includegraphics[trim={0.0cm 5cm 0cm 3cm},clip,width=1.0\textwidth]{figs/time_grid.pdf} \caption{Decomposition of time
domain into time windows.} \label{fig:slab_fig} \end{centering} 
\end{figure}
Over each time window, we introduce the space--time trial subspace,
$$\approxstate^n \in \stspace^n \subseteq \RR{N} \otimes \timeSpaceArg{n} , \qquad  n = 1,\ldots,\nslabs,$$ 
where $\approxstate^n :  [\timeStartArg{n} , \timeEndArg{n}] \rightarrow
\RR{\fomdim}$
is the \methodAcronym\ approximation to the state over the $n$th time window, $\timeSpaceArg{n}$ is the set of functions acting on $[\timeStartArg{n},\timeEndArg{n}]$, and  
$\timeStartArg{n}$ and $\timeEndArg{n}$ are the beginning and end of the $n$th
time window, respectively. Over each window, define the objective,
%\begin{equation}\label{eq:obj} \mathcal{J}^n(\stateArg{}{t}) = \frac{1}{2}
%\int_{\timeStartArg{n}}^{\timeEndArg{n}} \big[ \dot{\state}(\tau) -
%\velocity(\stateArg{}{\tau}) \big]^T \stweightingMatArg{n}(\tau) \big[
%\dot{\state}(\tau) - \velocity(\stateArg{}{\tau}) \big] d \tau,
%\end{equation}
\begin{equation}\label{eq:obj}
\begin{split} \mathcal{J}^n &\vcentcolon \statey \mapsto
\frac{1}{2} \int_{\timeStartArg{n}}^{\timeEndArg{n}} \big[ \dot{\statey}(t)
- \velocity(\stateyArg{}{t},t) \big]^T \stweightingMatArgt{n}{t} \big[
\dot{\statey}(t) - \velocity(\stateyArg{}{t},t) \big] d t \\
%&\vcentcolon \RR{\fomdim} \times [\timeStartArg{n},\timeEndArg{n}] \rightarrow
%\RR{}, \end{align}
&\vcentcolon \RR{\fomdim}\otimes \timeSpaceArg{n}  \rightarrow
\RR{}, 
\end{split}
\end{equation}
%\begin{align}\label{eq:obj} \mathcal{J}^n &\vcentcolon \state \mapsto
%\frac{1}{2} \int_{\timeStartArg{n}}^{\timeEndArg{n}} \resid(\state)^T
%\stweightingMat \resid(\state) d\tau \\ &\vcentcolon \RR{\fomdim} \times
%[0,T] \rightarrow \RR{}.  \end{align}
where $\stweightingMatArg{n} \equiv \stweightingMatOneArg{ }^T \stweightingMatOneArg{ } \in \RR{\fomdim \times \fomdim}$ is a
symmetric positive semi-definite matrix that, e.g., enables hyper-reduction and/or modifies the norm. For simplicity, 
it is assumed that the weighting matrix is the same for all time windows.

\methodAcronym\ computes a sequence of approximate solutions $\approxstateArgnt{n}$, for $n=1,\ldots,\nslabs$, as the solution to the minimization problems,
\begin{equation}\label{eq:tclsrm}
\begin{split}
      &\underset{\stateyArgnt{n} \in \stspace^n}{\text{minimize}} \; \mathcal{J}^n(\stateyArgnt{n}), \\
      &\text{subject to } \;  \stateyArg{n}{\timeStartArg{n}} =
\begin{cases}\mathbb{P}^n (\approxstateArgnt{n-1})(\timeEndArg{n-1}) & n = 2,\ldots,\nslabs \\
\mathbb{P}^n( \stateFOMArgnt{1})(0)& n=1, \end{cases} 
\end{split}
\end{equation}
%\methodAcronym\ computes a sequence of approximate solutions $\approxstateArgnt{n}$ as the solution to the minimization problem,
%\begin{equation}\label{eq:tclsrm}
%\begin{split}
%       &\approxstateArgnt{n} =  \underset{\statey \in \stspace^n}{\text{arg\,min}} \; \mathcal{J}^n(\statey), \\ 
%      &\text{subject to }\;  \approxstateArg{n}{\timeStartArg{n}} =
%\begin{cases}\mathbb{P}^n (\approxstateArgnt{n-1})(\timeEndArg{n-1}) & n = 2,\ldots,\nslabs \\
%\mathbb{P}^n( \stateFOMArgnt{1})(0)& n=1, \end{cases} 
%\end{split}
%\end{equation}
where $\mathbb{P}^n: \RR{N} \otimes \timeSpaceArg{n} \rightarrow \stspaceArg{n}$ is an orthogonal projection onto the 
trial subspace (e.g., $\elltwo$).
%\methodAcronym\ generates approximations to~\eqref{eq:FOM} by sequentially minimizing
%the FOM ODE residual over the trial space for each time slab.
%\methodAcronym\ is defined as follows,
%\begin{equation}\label{eq:tclsrm}
%\approxstate^n= \underset{\statey \in \stspace^n}{\text{arg\,min } }
%\mathcal{J}^n(\statey), \qquad n = 1,2,...,\nslabs,
%\end{equation}
% subject to
%the boundary condition, \begin{equation*} \approxstate^n(\timeStartArg{n}) =
%\begin{cases}\mathbb{P}^n \approxstate^{n-1}(\timeEndArg{n-1}) & n = 2,\ldots,\nslabs \\
%\mathbb{P}^n \stateFOMIC & n=1, \end{cases} \end{equation*}
%where $\mathbb{P}^n: \RR{N} \rightarrow \stspaceArg{n}$ projects onto the 
%trial space (e.g., an $L^2$ projector).
\begin{remark}
It is possible to construct the trial subspaces such that they have continuous support between time windows through the 
use of, e.g., affine transformations.
\end{remark}
%and 
%$\approxstate^n :  [\timeStartArg{n} , \timeEndArg{n}] \rightarrow
%\RR{\fomdim}$
%is the approximate solution over the $n$th time slab.% and $\approxstate_0 \in
%\RR{\fomdim}$ is the FOM initial condition
%projected onto the trial space; (e.g., via for $L^2$ projection).
We now define the trial subspaces $\stspaceArg{n}$. We consider \spatialAcronym\ trial subspaces and \spaceTimeAcronym\ trial subspaces. 
We leave further investigation into other trial subspaces, such as nonlinear manifolds~\cite{leeCarlberg}, as a subject for future work.
%A variety of trial spaces have been examined in the model-order reduction community.
%The most popular trial space comprises a linear, spatial-projection-only trial space (e.g., Eqns.~\eqref{eq:spatial_subspace}-\eqref{eq:spatial_subspace3}), although recently 
%nonlinear trial spaces~\cite{leeCarlberg} and space--time trial spaces~\cite{choi_stlspg,constantine_strom,2,3} have gained attention. This work focuses on the classic 
%spatial-projection-only trial space, and also briefly considers space--time trial spaces.
%We leave further investigation into other trial spaces as future work.

### 2019-09-19 section4/numerical_methods.tex
latest

\section{Numerical Solution Techniques}\label{sec:numerical_techniques}
The discussion to this point has outlined the formulation of the \methodAcronym\ method. We now consider numerical solution techniques. 
As \methodAcronym\ displays commonalities with optimal control problems, a large existing body of work can be leveraged. This section discuses a variety of such techniques and outlines how they can be used to solve the \methodAcronym\ system. We focus primarily on direct and indirect methods for \spatialAcronym\ trial spaces, 
and then briefly outline direct and indirect methods for \spaceTimeAcronym\ trial spaces. 
%Equation~\ref{eq:obj_gen_slab} displays commonalities with optimal control problems. For timeslabs $n = 1,\ldots,\nslabs$, the objective is to find the \textit{function} $\genstate^n(t)$ that minimizes the \textit{functional} $ \mathcal{J}^n$. The distinction between Eq.~\ref{eq:obj_gen_slab} and traditional optimal control problems is that, in the form presented in Eq.~\ref{eq:obj_gen_slab}, (1) there is not a controller and (2) there is no system that describes the dynamics for the generalized coordinates. 
%Techniques used to solve optimal control problems can be leveraged to solve Eq.~\ref{eq:obj_gen_slab} (or, equivalently, Eqs.~\eqref{eq:tclspg_oc1} and~\eqref{eq:tclspg_oc2}).

@@

In the present context, both direct and indirect methods are investigated to solve \methodAcronym\ with \spatialAcronym\ trial spaces. We consider:

>>>>

\section{Numerical Solution Techniques}\label{sec:numerical_techniques}
The discussion to this point has outlined the formulation of the \methodAcronym\ method. We now consider numerical solution techniques. 
As \methodAcronym\ displays commonalities with optimal control problems, a large existing body of work can be leveraged. This section discuses a variety of such techniques and outlines how they can be used to solve the \methodAcronym\ system. We focus primarily on direct and indirect methods for \spatialAcronym\ trial subspaces, 
and then briefly outline direct and indirect methods for \spaceTimeAcronym\ trial subspaces. 
%Equation~\ref{eq:obj_gen_slab} displays commonalities with optimal control problems. For timeslabs $n = 1,\ldots,\nslabs$, the objective is to find the \textit{function} $\genstate^n(t)$ that minimizes the \textit{functional} $ \mathcal{J}^n$. The distinction between Eq.~\ref{eq:obj_gen_slab} and traditional optimal control problems is that, in the form presented in Eq.~\ref{eq:obj_gen_slab}, (1) there is not a controller and (2) there is no system that describes the dynamics for the generalized coordinates. 
%Techniques used to solve optimal control problems can be leveraged to solve Eq.~\ref{eq:obj_gen_slab} (or, equivalently, Eqs.~\eqref{eq:tclspg_oc1} and~\eqref{eq:tclspg_oc2}).

@@

In the present context, both direct and indirect methods are investigated to solve \methodAcronym\ with \spatialAcronym\ trial subspaces. We consider:

### 2019-09-19 section4/spacetime_numerical.tex
latest

\subsection{\spaceTimeAcronym\ Trial Spaces: Direct and Indirect Methods}
We now briefly consider \spaceTimeAcronym\ trial spaces. 
For \spaceTimeAcronym\ trial spaces, the distinction between a direct and indirect method is less clear as the optimization variable (i.e., the generalized coordinates) are finite 
dimensional. There is no need to transcribe an infinite dimensional optimization variable into a finite dimensional one. There is, however, still a need to develop a finite 
dimensional representation of the objective function~\eqref{eq:obj_gen_slab}. In what follows, we describe two techniques to do this: one that works with the FOM O$\Delta$E and one that works with the FOM ODE. We associate direct methods as those 
that work with the O$\Delta$E and indirect methods with those that work directly with the continuous ODE.

@@

\begin{remark}
For the limiting case where the window size spans the entire domain, $\DeltaSlabArg{1}\equiv T$, direct \methodAcronym\ with a \spaceTimeAcronym\ trial space recovers ST-LSPG.
\end{remark}

@@

Leveraging these collocation points, the indirect method for \methodAcronym\ with a \spaceTimeAcronym\ trial space yields,

@@

\subsection{\spaceTimeAcronym\ Trial Space: Summary}
As was just shown, \spaceTimeAcronym\ trial spaces yield a series of space--time algebraic systems over each window. As a variety of work has examined space--time reduced-order models with \spaceTimeAcronym\ trial spaces, 
a detailed exposition of solution techniques for these systems is not pursued here. It is sufficient to say that the 
space--time trial space yields a series of dense (non)linear systems to be solved over each window.

>>>>

\subsection{\spaceTimeAcronym\ Trial Spaces: Direct and Indirect Methods}
We now briefly consider \spaceTimeAcronym\ trial subspaces. 
For \spaceTimeAcronym\ trial subspaces, the distinction between a direct and indirect method is less clear as the optimization variable (i.e., the generalized coordinates) are finite 
dimensional. There is no need to transcribe an infinite dimensional optimization variable into a finite dimensional one. There is, however, still a need to develop a finite 
dimensional representation of the objective function~\eqref{eq:obj_gen_slab}. In what follows, we describe two techniques to do this: one that works with the FOM O$\Delta$E and one that works with the FOM ODE. We associate direct methods as those 
that work with the O$\Delta$E and indirect methods with those that work directly with the continuous ODE.

@@

\begin{remark}
For the limiting case where the window size spans the entire domain, $\DeltaSlabArg{1}\equiv T$, direct \methodAcronym\ with a \spaceTimeAcronym\ trial subspace recovers ST-LSPG.
\end{remark}

@@

Leveraging these collocation points, the indirect method for \methodAcronym\ with a \spaceTimeAcronym\ trial subspace yields,

@@

\subsection{\spaceTimeAcronym\ Trial Space: Summary}
As was just shown, \spaceTimeAcronym\ trial subspaces yield a series of space--time algebraic systems over each window. As a variety of work has examined space--time reduced-order models with \spaceTimeAcronym\ trial subspaces, 
a detailed exposition of solution techniques for these systems is not pursued here. It is sufficient to say that the 
space--time trial subspace yields a series of dense (non)linear systems to be solved over each window.
